---
title: "Shiny Application Reproducible Pitch Presentation"
author: "JH"
date: "7/28/2021"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r, echo=FALSE,message=FALSE}
library(dplyr)

```


## App Introduction
This App is used for checking the performance statistics of James Harden, a NBA player, in his career so far.

The App can be accessed from the followed link: <https://jliao12.shinyapps.io/example/>

The app.R file can be found as follow : <https://github.com/jliao12/hiny-Application-and-Reproducible-Pitch-Project/blob/master/ExampleApp/app.R>

## Overview of data
```{r,echo=FALSE,message=FALSE}
library(plotly)
library(reshape2)
library(dplyr)
library(grid)
h_r <- read.csv(url("https://raw.githubusercontent.com/jliao12/hiny-Application-and-Reproducible-Pitch-Project/master/original_data/harden_regular.csv"))
h_p <- read.csv(url("https://raw.githubusercontent.com/jliao12/hiny-Application-and-Reproducible-Pitch-Project/master/original_data/harden_playoff.csv"))
season_list <- h_r[,"Season"]
row.names(h_r) <- season_list
row.names(h_p) <- season_list
h_r <- mutate(h_r,year = seq(2009,2020,1))
h_p <- mutate(h_p,year = seq(2009,2020,1))
h_r$FGP <- h_r$FGP*100
h_p$FGP <- h_p$FGP*100
h_r_s <- h_r[,c("G","PTS","FGP","AST","STL","TRB","year")]
h_p_s <- h_p[,c("G","PTS","FGP","AST","STL","TRB","year")]
h_r_s_m <- melt(h_r_s,id.vars = "year",variable.name = "stat",value.name = "value")
h_p_s_m <- melt(h_p_s,id.vars = "year",variable.name = "stat",value.name = "value")
h_r_s_m <- mutate(h_r_s_m,cato = rep("Regular",72))
h_p_s_m <- mutate(h_p_s_m,cato = rep("Playoff",72))
mix <- rbind(h_r_s_m,h_p_s_m)
la <- c("2010-11","2012-13","2014-15","2016-17","2018-19","2020-21")
head(h_r_s)
head(h_p_s)
```


## Panel Introduction

<font size="4"> In side panel, you can select the following options:   

- **Season:** can select from 2009-10 season to 2020-21 season
- **Regular or Playoffs:** can select the regular season or playoffs
- **Statistics:** six main stats are listed for you to choose
- **Years to Forecast** slide input the number of future years to forecast the pts performance.  

The main panel has two tabs, the Overview tab has three sections: 

- **Head:** the head will display the season and stages you choose
- **Table:** the table will display the stats you choose in that season and stage
- **Plots:** the plots will display the changing of the stats you choose. The yellow vertical line will indicate the season you choose 

The forecast tab display the PTS forecast plot and the 95% confidence interval of PTS.</font>

## Plots Sample
```{r,echo=FALSE}
library(reshape2)
ggplotly(ggplot(mix,aes(x = year, y = value, colour = cato)) +
                         geom_point(size = 1,shape = 1) + 
                         facet_wrap(~stat,scales = "free") + 
                         theme(panel.spacing.x=unit(0.5, "lines"),
                               panel.spacing.y=unit(2, "lines"),
                               axis.ticks = element_blank(),
                               axis.text.x = element_text(angle = 30,size = 6),
                               axis.text.y =  element_text(size = 6)) +
                         scale_x_continuous(breaks = c(2010,2012,2014,2016,2018,2020),
                                            labels= la) + 
                         xlab(NULL)
                     
            ) %>% layout(legend = list(orientation = "h", x = 0.35, y = -0.2))

```
