---
title: "Shiny Application Reproducible Pitch Presentation"
author: "JH"
date: "7/28/2021"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Instructions

This peer assessed assignment has two parts. First, you will create a Shiny application and deploy it on Rstudio's servers. Second, you will use Slidify or Rstudio Presenter to prepare a reproducible pitch presentation about your application. 

The detailed instructions can be found online.

## App Introduction
This App is used for checking the performance statistics of James Harden, a NBA player, in his career so far.

The App can be accessed from the followed link: <https://jliao12.shinyapps.io/example/>

The app.R file can be found as follow : <http://rmarkdown.rstudio.com>



## Side Panel Introduction

In side panel, you can select the following options:  

- **Season:** can select from 2009-10 season to 2020-21 season
- **Regular or Playoffs:** can select the regular season or playoffs
- **Statistics:** six main stats are listed for you to choose

By selecting the three options, you can get the specific stats in specific season and specific stages

## Main Panel Introduction

The main panel has three sections as well:   

- **Head:** the head will display the season and stages you choose
- **Table:** the table will display the stats you choose in that season and stage
- **Plots:** the plots will display the changing of the stats you choose along the 12 years of James Harden's career. The yellow vertical line will indicate the season you choose 

## Slide with Plot

```{r pressure}
plot(pressure)
```

